Disambiguating Monocular Depth Estimation with a Single Transient

### 2020-07-09 paper/eccv2020CR/sections/introduction.tex
Minor changes and added citation

Here, we propose to use a single-pixel time-resolved detector and pulsed light
source in an unconventional way: rather than optically focusing them to record
the distance to a single scene point, we diffuse the emitted light and aggregate
the reflected light over the entire scene with the detector. \edit{The resulting
transient measurement resembles a histogram of the scene and can be used to
achieve accurate absolute depth in conjunction with a monocular depth estimate}
(Fig.~\ref{fig:teaser}).

@@

In summary, we make the following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth transient
    aggregated by a time-resolved detector to address scale ambiguity in MDE.
  \item \edit{We introduce a depth reconstruction algorithm that uses the
    detector's image formation model in conjunction with a modified version of
    histogram matching, to produce a depth map from a single RGB image and
    transient. The algorithm can be applied instantly to any existing and
    future MDE algorithms.}
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset
    and demonstrate that our approach is able to resolve scale ambiguity while
    being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data,
    assessing both the quality and the ability of our method to help
    generalization of monocular depth estimators across scene types.
\end{itemize}

>>>>

Here, we propose to use a single-pixel time-resolved detector and pulsed light
source in an unconventional way: rather than optically focusing them to record
the distance to a single scene point, we diffuse the emitted light and aggregate
the reflected light over the entire scene with the detector. \edit{The resulting
transient measurement resembles a histogram of the scene's depth and can be used to
achieve accurate absolute depth in conjunction with a monocular depth estimate}
(Fig.~\ref{fig:teaser}).

@@

In summary, we make the following contributions:
%
\begin{itemize}
	\item We propose augmenting an RGB camera with a global depth transient
    aggregated by a time-resolved detector to address scale ambiguity in MDE.
  \item \edit{We introduce a depth reconstruction algorithm that uses the
    detector's image formation model in conjunction with a modified version of
    histogram matching, to produce a depth map from a single RGB image and
    transient. The algorithm can be applied instantly to any existing and
    future MDE algorithms.}
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset
    and demonstrate that our approach is able to resolve scale ambiguity while
    being fast and easy to implement.
	\item We build a prototype camera and evaluate its efficacy on captured data,
    assessing both the quality and the ability of our method to improve generalization of monocular depth estimators across scene types.
\end{itemize}
